Abstraction Refinement for Emptiness Checking of Alternating Data Automata

### 2018-02-05 tacas/draft.tex
ok

\paragraph{\em Example} 
The following sequence is a non-accepting run of the ADA from Figure
\ref{fig:ex} on the word
$(a,\tuple{0,0}),(a,\tuple{1,1}),(b,\tuple{2,1})$, where $\Data^\I =
\zed$ and the function symbols have standard arithmetic
interpretation:
\[\begin{array}{l}
q_0 \stackrel{(a,\tuple{0,0})}{\Longrightarrow} 
q_1 \wedge q_2 \wedge x_1\teq0 \wedge y_1\teq0 \stackrel{(a,\tuple{1,1})}{\Longrightarrow} \\ 
\underbrace{q_1 \wedge q_2 \wedge x_2\teq y_1+1 \wedge y_2\teq x_1+1}_{q_1} ~\wedge~
\underbrace{q_2 \wedge x_2>x_1 \wedge y_2>y_1}_{q_2} \\ 
\wedge~ x_1\teq0 \wedge y_1\teq0 \stackrel{(b,\tuple{2,1})}{\Longrightarrow} 
\underbrace{q_3 \wedge x_2\geq y_2}_{q_1} \wedge \underbrace{q_4 \wedge x_2>y_2}_{q_2} \wedge x_2\teq y_1+1 \\ 
\wedge~ y_2\teq x_1+1 \wedge \underbrace{q_4 \wedge x_2>y_2}_{q_2} \wedge x_2>x_1 \wedge y_2>y_1 \wedge x_1\teq0 \wedge y_1\teq0 ~\hfill\text{\qed}
\end{array}\]

>>>>

\paragraph{\em Example} 
The following sequence is a non-accepting run of the ADA from Figure
\ref{fig:ex} on the word
$(a,\tuple{0,0}),(a,\tuple{1,1}),(b,\tuple{2,1})$, where $\Data^\I =
\zed$ and the function symbols have standard arithmetic
interpretation:
{\scriptsize\[\begin{array}{l}
q_0 \stackrel{(a,\tuple{0,0})}{\Longrightarrow} 
q_1 \wedge q_2 \wedge x_1\teq0 \wedge y_1\teq0 \stackrel{(a,\tuple{1,1})}{\Longrightarrow} 
\underbrace{q_1 \wedge q_2 \wedge x_2\teq y_1+1 \wedge y_2\teq x_1+1}_{q_1} ~\wedge~
\underbrace{q_2 \wedge x_2>x_1 \wedge y_2>y_1}_{q_2} 
\wedge~ x_1\teq0 \wedge y_1\teq0 \stackrel{(b,\tuple{2,1})}{\Longrightarrow} \\
\underbrace{q_3 \wedge x_2\geq y_2}_{q_1} \wedge \underbrace{q_4 \wedge x_2>y_2}_{q_2} \wedge x_2\teq y_1+1 
\wedge~ y_2\teq x_1+1 \wedge \underbrace{q_4 \wedge x_2>y_2}_{q_2} \wedge x_2>x_1 \wedge y_2>y_1 \wedge x_1\teq0 \wedge y_1\teq0 ~\hfill\text{\qed}\end{array}\]}
